### 2024-07-24 doc/Thesis/chapter/03-experimental.tex
finish editing 03

%The first 200 recipes were optimized via biotic refinforcement learning (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%The main part of all samples (200 out of 244) were pre-optimization samples,  from which the bulk were screening experiments optimized via biotic reinforcement learning  (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%Initially, glass plates were doctor bladed manually with aqueous solution and calcinated 
%via HP1. 
%Glass was used because of its availability and in order to be able to make IR 
%\td{transmission} spectra.
%In order to measure the resistivity of the produced layer \gls{fto} and \gls{ito} layered 
%glass plates (both conductive) were used as substrate.
%Conducting substrates were also needed to produce \gls{sem} micrographs. 
%\td{should maybe put this into beginning of section \ref{sec:exp}?}
%otherwise the sample would charge and can't be pictured anymore. 
%this means if the produced layer is thick and homogeneous enough, it's difficult to see in sem
%Different additives were included in the recipe (see table \ref{tab:rec1}) and the resistance was checked with a multimeter. 
%\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
%Composition of the \td{aqueous solution (I thought this did not work?)}, heating program, blade distance (distance between blade and substrate) and layer count were varied but no homogeneous layers resulted. 
%The buthanolic recipe was introduced, which gave rise to homogeneous films.
%\td{After the blade moved over the substrate the remaining liquid needed about a minute to evaporate at room temperature. (2x mentioned this before!)}
%\td{
%The then current procedure resulted in clear and continuous films, but was plagued from inhomogeneities due to drying stains. 
%The drying stains could be circumvented by using a heat gun, but the results were not reproducible. 
The glass plate of the film applicator was exchanged with a metal plate.
This allowed to hold the sample in place through underpressure and control temperature. 
The bounds of the process variables were then explored in a preliminary study 
using the Plackett-Burman\cite{Plackett1946} design implemented in the \texttt{python3} (version 3.9)
library \texttt{pyDOE} (version 0.3.8); 
with 
(1,5), (4,10), (400,500), (120,480), (0.1,5) and  (20,80) 
as nominal and extreme values for 
relative concentration of Zr $c_{zr}$, number of coating layers $n_L$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see appendix \ref{sec:app-pre-emma}).
\ds{
table \ref{tab:pre-opt1}).
\begin{table}[hbt]
	\centering
	\caption{Pre-optimization experiments \td{(still smaller?? why? what am I supposed to learn?)} }
	\label{tab:pre-opt}
	\begin{subtable}{0.5\linewidth}
		\centering
		\subcaption{Placket-Burman style experiments}
		\label{tab:pre-opt1}
		\begin{tabular}{cccccc}
			\hline
			\hline
	%		&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
			$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
			\hline
	1	&10	&5	&20	&120	&400	\\
	1	&4	&0.1	&20	&120	&500	\\
	5	&10	&0.1	&20	&120	&500	\\
	5	&4	&5	&20	&480	&400	\\
	1	&5	&5	&80	&120	&500	\\
	1	&10	&1	&80	&480	&400	\\
	5	&5	&1	&80	&120	&400	\\
	5	&10	&5	&80	&480	&500	\\
			\hline\hline
		\end{tabular}
	\end{subtable}%
	\begin{subtable}{0.5\linewidth}
		\centering
        \subcaption{Hand picked experiments; $^*$varied stabilization agent}
		\label{tab:pre-opt2}
		\begin{tabular}{cccccc}
	%conc	&layers	&vDOC	&TDOC	&vCal	&Tcal		\\
			\hline\hline
			$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
	%conc	&layers	&$v_{\textrm{C}}$	&$T_{\textrm{C}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
			\hline
	2	&8	&0.5	&40	&360	&470	\\
	2	&6	&2	&40	&360	&430	\\
	1	&4	&12	&70	&120	&500	\\
	1	&9	&18	&80	&240	&400	\\
	4$^*$	&6	&14	&60	&240	&500	\\
%	4$^\dagger$	&6	&14	&60	&240	&500	\\
%	4$^\ddagger$	&6	&14	&60	&240	&500	\\
			\hline
			\hline
			\\ \\  \\
%			\multicolumn{6}{c}{*different stabilization reagent compositions}\\
		\end{tabular}
	\end{subtable}
\end{table}
}

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
because of much better solution stability and similar electric properties of resulting layers (how did you test this?? see appendix \ref{sec:app-pre-emma}).
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable passivization results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

>>>>

%The first 200 recipes were optimized via biotic refinforcement learning (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%The main part of all samples (200 out of 244) were pre-optimization samples,  from which the bulk were screening experiments optimized via biotic reinforcement learning  (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%Initially, glass plates were doctor bladed manually with aqueous solution and calcinated 
%via HP1. 
%Glass was used because of its availability and in order to be able to make IR 
%\td{transmission} spectra.
%In order to measure the resistivity of the produced layer \gls{fto} and \gls{ito} layered 
%glass plates (both conductive) were used as substrate.
%Conducting substrates were also needed to produce \gls{sem} micrographs. 
%\td{should maybe put this into beginning of section \ref{sec:exp}?}
%otherwise the sample would charge and can't be pictured anymore. 
%this means if the produced layer is thick and homogeneous enough, it's difficult to see in sem
%Different additives were included in the recipe (see table \ref{tab:rec1}) and the resistance was checked with a multimeter. 
%\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
%Composition of the \td{aqueous solution (I thought this did not work?)}, heating program, blade distance (distance between blade and substrate) and layer count were varied but no homogeneous layers resulted. 
%
%The buthanolic recipe was introduced, which gave rise to homogeneous films.
%\td{After the blade moved over the substrate the remaining liquid needed about a minute to evaporate at room temperature. (2x mentioned this before!)}
%\td{
%The then current procedure resulted in clear and continuous films, but was plagued from inhomogeneities due to drying stains. 
%The drying stains could be circumvented by using a heat gun, but the results were not reproducible.

%starting with pre-optimisation
%The glass plate of the film applicator was exchanged with a metal plate.
A metal plate with vacuum chuck and temperature control was used as a base in the film applicator. 
%This allowed to hold the sample in place through underpressure and control temperature. 
The bounds of the process variables were then explored in a preliminary study 
using the Plackett-Burman\cite{Plackett1946} design implemented in the \texttt{python3} (version 3.9)
library \texttt{pyDOE} (version 0.3.8); 
with 
(1,5), (4,10), (400,500), (120,480), (0.1,5) and  (20,80) 
as nominal and extreme values for 
relative concentration of Zr $c_{zr}$, number of coating layers $n_L$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} speed $v_{C}$[\mm{}/\s{}] and \gls{db} temperature $T_{C}$[\oc{}], respectively.
After testing the first samples, the lower limit for \gls{db} speed was altered from 0.1 to 1 (see appendix \ref{sec:app-pre-emma}).
%
\ds{
table \ref{tab:pre-opt1}).
\begin{table}[hbt]
	\centering
	\caption{Pre-optimization experiments \td{(still smaller?? why? what am I supposed to learn?)} }
	\label{tab:pre-opt}
	\begin{subtable}{0.5\linewidth}
		\centering
		\subcaption{Placket-Burman style experiments}
		\label{tab:pre-opt1}
		\begin{tabular}{cccccc}
			\hline
			\hline
	%		&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
			$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
			\hline
	1	&10	&5	&20	&120	&400	\\
	1	&4	&0.1	&20	&120	&500	\\
	5	&10	&0.1	&20	&120	&500	\\
	5	&4	&5	&20	&480	&400	\\
	1	&5	&5	&80	&120	&500	\\
	1	&10	&1	&80	&480	&400	\\
	5	&5	&1	&80	&120	&400	\\
	5	&10	&5	&80	&480	&500	\\
			\hline\hline
		\end{tabular}
	\end{subtable}%
	\begin{subtable}{0.5\linewidth}
		\centering
        \subcaption{Hand picked experiments; $^*$varied stabilization agent}
		\label{tab:pre-opt2}
		\begin{tabular}{cccccc}
	%conc	&layers	&vDOC	&TDOC	&vCal	&Tcal		\\
			\hline\hline
			$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
	%conc	&layers	&$v_{\textrm{C}}$	&$T_{\textrm{C}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\
			\hline
	2	&8	&0.5	&40	&360	&470	\\
	2	&6	&2	&40	&360	&430	\\
	1	&4	&12	&70	&120	&500	\\
	1	&9	&18	&80	&240	&400	\\
	4$^*$	&6	&14	&60	&240	&500	\\
%	4$^\dagger$	&6	&14	&60	&240	&500	\\
%	4$^\ddagger$	&6	&14	&60	&240	&500	\\
			\hline
			\hline
			\\ \\  \\
%			\multicolumn{6}{c}{*different stabilization reagent compositions}\\
		\end{tabular}
	\end{subtable}
\end{table}
}

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
because of much better solution stability and similar electric properties of resulting layers (how did you test this?? see appendix \ref{sec:app-pre-emma}).
The best process after this set of experiments was chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable electric insulation results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi
